Sequence Specific Modeling of Cell-Free Protein Synthesis

### 2017-03-08 Paper_v1.tex
Changes to MM

We also calculated the carbon yield for each protein (Fig.~\ref{fig:Yield}A).

@@

The bounds on the transcription rate ($\mathcal{L}_{TX}=w_{TX}=\mathcal{U}_{TX}$) was modeled as:
\begin{equation}
	w_{TX} = V_{TX}^{max}\left(\frac{G}{K_{TX}+G}\right)
\end{equation}
where $G$ denotes the gene concentration and $K_{TX}$ denotes a transcription saturation coefficient.
The maximum rate of transcription $V_{TX}^{max}$ was formulated as:
\begin{equation}
	V_{TX}^{max} \equiv \left[R_{T}\left(\frac{v_{TX}}{l_{G}}\right)u\left(\kappa\right)\right]
\end{equation}
The term $R_{T}$ denotes the RNA polymerase concentration (nM),
$v_{TX}$ denotes the RNA polymerase elongation rate (nt/h),
$l_{G}$ denotes the gene length in nucleotides (nt).
The term $u\left(\kappa\right)$ (dimensionless, $0\leq u\left(\kappa\right)\leq 1$) describes a model of promoter activity, where $\kappa$ denotes promoter specific parameters.
The forms for the promoter models were taken from Moon $\emph{et~al.}$ \cite{Moon:2012ab}.
In this study, we considered two promoters: T7 and $\sigma_{70}$.
The promoter function for the T7 promoter, $u_{T7}$, was given by:
\begin{equation}
	u_{T7} = \frac{K_{T7}}{1 + K_{T7}}
\end{equation}
where $K_{T7}$ denotes a T7 RNA polymerase binding constant.
The $\sigma_{70}$ promoter function $u_{\sigma_{70}}$ (which was used for all other proteins) was formulated as:
\begin{equation}
	u_{\sigma_{70}} = \frac{K_{1}+K_{2}f_{\sigma_{70}}}{1 + K_{1}+K_{2}f_{\sigma_{70}}}
\end{equation}
where $K_{1}$ denotes the weight of RNA polymerase binding alone,
$K_{2}$ denotes the weight of RNAP-$\sigma_{70}$ bound to the promoter,
and $f_{p70}$ denotes the fraction of the $\sigma_{70}$ transcription factor bound to RNAP (modeled as a Hill function).
The values for $K_{T7}, K_{1}$, $K_{2}$ and $f_{\sigma_{70}}$, along with all other promoter parameters, are given in Table ZZ.

>>>>

The mean carbon yield was inversely proportional to protein size and varied between 40-55\% for the proteins sampled (Fig.~\ref{fig:Yield}).

@@

The bounds on the transcription rate ($\mathcal{L}_{TX}=w_{TX}=\mathcal{U}_{TX}$) were modeled as:
\begin{equation}
	w_{TX} = V_{TX}^{max}\left(\frac{G}{K_{TX}+G}\right)
\end{equation}
where $G$ denotes the gene concentration and $K_{TX}$ denotes a transcription saturation coefficient.
The maximum rate of transcription $V_{TX}^{max}$ was formulated as:
\begin{equation}
	V_{TX}^{max} \equiv \left[R_{T}\left(\frac{v_{TX}}{l_{G}}\right)u\left(\kappa\right)\right]
\end{equation}
The term $R_{T}$ denotes the RNA polymerase concentration (nM),
$v_{TX}$ denotes the RNA polymerase elongation rate (nt/h),
$l_{G}$ denotes the gene length in nucleotides (nt).
The term $u\left(\kappa\right)$ (dimensionless, $0\leq u\left(\kappa\right)\leq 1$) describes a model of promoter activity, where $\kappa$ denotes promoter specific parameters.
The forms for the promoter models were taken from Moon $\emph{et~al.}$ \cite{Moon:2012ab}.
In this study, we considered two promoters: T7 and $\sigma_{70}$.
The promoter function for the T7 promoter, $u_{T7}$, was given by:
\begin{equation}
	u_{T7} = \frac{K_{T7}}{1 + K_{T7}}
\end{equation}
where $K_{T7}$ denotes a T7 RNA polymerase binding constant.
The $\sigma_{70}$ promoter function $u_{\sigma_{70}}$ (which was used for all other proteins) was formulated as:
\begin{equation}
	u_{\sigma_{70}} = \frac{K_{1}+K_{2}f_{\sigma_{70}}}{1 + K_{1}+K_{2}f_{\sigma_{70}}}
\end{equation}
where $K_{1}$ denotes the weight of RNA polymerase binding alone,
$K_{2}$ denotes the weight of RNAP-$\sigma_{70}$ bound to the promoter,
and $f_{p70}$ denotes the fraction of the $\sigma_{70}$ transcription factor bound to RNAP (modeled as a Hill function).
The values for $K_{T7}, K_{1}$, $K_{2}$ and $f_{\sigma_{70}}$, along with all other promoter parameters, are given in Table ZZ.
